Examining the critical path neighborhood for flexible job shop problems

### 2016-01-26 paper/paper.tex
some paper updates

The rest of the instances were generated using a random instance generator built for this purpose. These are labeled \emph{v20 -- v33}. The optimal makespans for these instances is unknown. However, they do provide insight into the convergence behavior, especially when compared between instances.

@@

\begin{table}
\centering
\footnotesize
\begin{tabular}{@{\bfseries}rrrrrrrrrrrr}
	\toprule
	\multicolumn{4}{c}{Instance} & \multicolumn{2}{c}{Properties} && \multicolumn{5}{c}{Results} \\
	\cmidrule(r){1-4} \cmidrule(lr){5-6} \cmidrule(lr){8-12}
	\normalfont{name} & $|\mathcal{J}|$ & $|\mathcal{T}|$ & $|\mathcal{M}|$ & $\max C_\text{job}$ &
	$C_\text{opt}$ && $\alpha$ & restarts & $\bar{C}$ & $C_\text{best}$ & $\bar{t}$ \\
	\midrule
	ft06 &  6 &  6 &  6 &   47 &   55 &&    0.9 & 1 &   55 &   55 &    0 \\
	ft10 & 10 & 10 & 10 &  655 &  930 &&    0.9 & 5 &  954 &  941 &    2 \\
	     &    &    &    &      &      &&   0.99 & 5 &  943 &  938 &   18 \\
	     &    &    &    &      &      &&  0.999 & 5 &  933 &  930 &  182 \\
	ft20 & 20 &  5 &  5 &  387 & 1165 &&    0.9 & 5 & 1215 & 1186 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 & 1182 & 1178 &   13 \\
	     &    &    &    &      &      &&  0.999 & 5 & 1170 & 1165 &  130 \\[2ex]
	c1   &  4 &  2 &  4 &   34 &   34 &&    0.9 & 1 &   34 &   34 &    0 \\
	c2   &  4 &  2 &  4 &   53 &   53 &&    0.9 & 1 &   53 &   53 &    0 \\
	c3   &  4 &  2 &  4 &  133 &  143 &&    0.9 & 1 &  143 &  143 &    0 \\
	c4   &  6 &  2 &  4 &   52 &   57 &&   0.99 & 5 &   57 &   57 &    2 \\
	c5   &  6 &  2 &  4 &  105 &  113 &&   0.99 & 5 &  113 &  113 &    2 \\
	c6   &  6 &  2 &  4 &  205 &  225 &&   0.99 & 5 &  225 &  225 &    2 \\
	c7   &  4 &  3 &  9 &   39 &   39 &&    0.9 & 1 &   39 &   39 &    0 \\
	c8   &  4 &  3 &  9 &   64 &   64 &&    0.9 & 1 &   64 &   64 &    0 \\
	c9   &  4 &  3 &  9 &  138 &  138 &&    0.9 & 1 &  138 &  138 &    0 \\
	c10  &  6 &  3 &  9 &   50 &   50 &&    0.9 & 1 &   50 &   50 &    0 \\
	c11  &  6 &  3 &  9 &  103 &  103 &&    0.9 & 1 &  103 &  103 &    0 \\
	c12  &  6 &  3 &  9 &  204 &  204 &&    0.9 & 1 &  204 &  204 &    0 \\
	c13  &  8 &  3 &  9 &  337 &  337 &&    0.9 & 5 &  337 &  337 &    0 \\
	c14  &  8 &  3 &  9 &  705 &  705 &&    0.9 & 5 &  705 &  705 &    0 \\
	c15  &  8 &  3 &  9 & 1458 & 1458 &&    0.9 & 5 & 1458 & 1458 &    0 \\
	c16  & 10 &  4 & 16 &  405 &  405 &&    0.9 & 5 &  405 &  405 &    0 \\
	c17  & 10 &  4 & 16 &  955 &  955 &&    0.9 & 5 &  955 &  955 &    0 \\
	c18  & 10 &  4 & 16 & 1621 & 1621 &&    0.9 & 5 & 1621 & 1621 &    0 \\
	c19  & 15 &  5 & 25 & 2631 & 2631 &&    0.9 & 5 & 2631 & 2631 &    0 \\[2ex]
	v20  &  8 &  2 &  4 &  176 &      &&    0.9 & 5 &  387 &  387 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 &  387 &  387 &    7 \\
	     &    &    &    &      &      &&  0.999 & 5 &  387 &  387 &   67 \\
	v21  &  8 &  2 &  8 &  187 &  187 &&    0.9 & 5 &  204 &  188 &    0 \\
	     &    &    &    &      &      &&   0.99 & 5 &  197 &  188 &    4 \\
	     &    &    &    &      &      &&  0.999 & 5 &  188 &  187 &   25 \\
	v22  &  8 &  4 &  8 &  195 &      &&    0.9 & 5 &  237 &  237 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 &  237 &  237 &    9 \\
	     &    &    &    &      &      &&  0.999 & 5 &  237 &  237 &   82 \\
	v30  & 16 &  2 &  4 &  666 &      &&    0.9 & 5 & 2382 & 2381 &   10 \\
	     &    &    &    &      &      &&   0.99 & 5 & 2381 & 2381 &  102 \\
	     &    &    &    &      &      &&  0.999 & 5 & 2381 & 2381 & 1045 \\
	v31  & 16 &  2 &  8 &  566 &      &&    0.9 & 5 &  963 &  961 &   12 \\
	     &    &    &    &      &      &&   0.99 & 5 &  960 &  959 &  126 \\
	     &    &    &    &      &      &&  0.999 & 5 &  958 &  956 & 1238 \\
	v32  & 16 &  4 &  8 &  655 &      &&    0.9 & 5 & 1119 & 1116 &   11 \\
	     &    &    &    &      &      &&   0.99 & 5 & 1112 & 1111 &  116 \\
	     &    &    &    &      &      &&  0.999 & 5 & 1108 & 1106 & 1164 \\
	v33  & 16 &  4 & 16 &  626 &  626 &&    0.9 & 5 &  628 &  626 &    5 \\
	     &    &    &    &      &      &&   0.99 & 5 &  657 &  651 &   84 \\
	\bottomrule
\end{tabular}
\caption{Computational results for the FJS}
\label{table:fjs}
\end{table}

@@

\begin{table}
\centering
\footnotesize
\begin{tabular}{@{\bfseries}rrrrrrrrrrrrr}
	\toprule
	& FJS & FBJS & && \multicolumn{2}{c}{Critical Path} &&
	\multicolumn{2}{c}{Naive shift} && \multicolumn{2}{c}{Both} \\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){6-7}
	\cmidrule(lr){9-10} \cmidrule(lr){12-13}
	\normalfont{name} & $C_\text{best}$ & $C_\text{opt}$ & $\alpha$ && $\bar{C}$ & $C_\text{best}$ &&
	$\bar{C}$ & $C_\text{best}$ && $\bar{C}$ & $C_\text{best}$ \\
	\midrule
	ft06 &   55 &   63 &  0.99 &&  102 &   95 &&   64 &   63 &&   66 &   63 \\
	ft10 &  930 & 1068 &   0.9 && 2183 & 1931 && 1507 & 1436 && 1464 & 1415 \\
	     &      &      &  0.99 && 2139 & 1931 && 1444 & 1353 && 1413 & 1349 \\
	     &      &      & 0.999 && 2366 & 2028 && 1380 & 1281 && 1371 & 1292 \\
	ft20 & 1165 &      &   0.9 && 2476 & 2406 && 1957 & 1866 && 1935 & 1869 \\
	     &      &      &  0.99 && 2454 & 2348 && 1840 & 1814 && 1860 & 1840 \\
	     &      &      & 0.999 && 2393 & 2209 && 1694 & 1646 && 1714 & 1632 \\[2ex]
	c1   &   34 &      &  0.99 &&   66 &   62 &&   37 &   37 &&   37 &   37 \\
	c2   &   53 &      &  0.99 &&   88 &   75 &&   65 &   65 &&   65 &   65 \\
	c3   &  143 &      &  0.99 &&  206 &  206 &&  180 &  180 &&  180 &  180 \\
	c4   &   57 &      &  0.99 &&  116 &  109 &&   94 &   92 &&   91 &   90 \\
	c5   &  113 &      &  0.99 &&  247 &  215 &&  180 &  170 &&  175 &  170 \\
	c6   &  225 &      &  0.99 &&  502 &  434 &&  365 &  360 &&  360 &  353 \\
	c7   &   39 &   39 &  0.99 &&   39 &   39 &&   39 &   39 &&   39 &   39 \\
	c8   &   64 &   64 &  0.99 &&   64 &   64 &&   64 &   64 &&   64 &   64 \\
	c9   &  138 &  138 &  0.99 &&  138 &  138 &&  138 &  138 &&  138 &  138 \\
	c10  &   50 &   50 &  0.99 &&   50 &   50 &&   50 &   50 &&   50 &   50 \\
	c11  &  103 &      &  0.99 &&  170 &  116 &&  106 &  106 &&  106 &  106 \\
	c12  &  204 &      &  0.99 &&  265 &  210 &&  208 &  208 &&  208 &  208 \\
	c13  &  337 &      &  0.99 &&  557 &  524 &&  467 &  458 &&  393 &  389 \\
	c14  &  705 &      &  0.99 && 1203 & 1036 &&  866 &  833 &&  797 &  788 \\
	c15  & 1458 &      &  0.99 && 2556 & 2258 && 1789 & 1666 && 1508 & 1493 \\
	c16  &  405 &  405 &  0.99 &&  519 &  483 &&  444 &  429 &&  405 &  405 \\
	c17  &  955 &  955 &  0.99 && 1257 & 1009 &&  962 &  955 &&  955 &  955 \\
	c18  & 1621 & 1621 &  0.99 && 2314 & 2131 && 1710 & 1688 && 1621 & 1621 \\
	c19  & 2631 & 2631 &  0.99 && 4568 & 3973 && 4365 & 4049 && 2631 & 2631 \\[2ex]
	v20  &  387 &      &   0.9 &&  571 &  540 &&  494 &  476 &&  438 &  423 \\
	     &      &      &  0.99 &&  527 &  517 &&  447 &  421 &&  424 &  418 \\
	v21  &  187 &      &   0.9 &&  331 &  293 &&  277 &  254 &&  218 &  215 \\
	     &      &      &  0.99 &&  327 &  291 &&  213 &  209 &&  198 &  194 \\
	v22  &  237 &      &   0.9 &&  419 &  387 &&  326 &  314 &&  294 &  284 \\
	     &      &      &  0.99 &&  393 &  369 &&  293 &  281 &&  273 &  262 \\
	v30  & 2381 &      &   0.9 && 4210 & 4068 && 5969 & 5856 && 3546 & 3438 \\
	     &      &      &  0.99 && 4200 & 4154 && 5591 & 5411 && 3287 & 3147 \\
	v31  &  959 &      &   0.9 && 1658 & 1573 && 4303 & 4133 && 1702 & 1635 \\
	     &      &      &  0.99 && 1688 & 1632 && 3772 & 3712 && 1646 & 1617 \\
	v32  & 1111 &      &   0.9 && 2570 & 2389 && 5214 & 5054 && 2570 & 2389 \\
	     &      &      &  0.99 && 2629 & 2601 && 4481 & 4209 && 2171 & 1983 \\
	v33  &  626 &      &   0.9 && 1296 & 1212 && 3182 & 2931 && 1098 & 1053 \\
	     &      &      &  0.99 && 1335 & 1244 && 2061 & 1903 &&  952 &  894 \\
	\bottomrule
\end{tabular}
\caption{Computational results for the FBJS}
\label{table:fbjs}
\end{table}

>>>>

The rest of the instances were generated using a random instance generator built for this purpose. These are labeled \emph{v20 -- v40}. The optimal makespans for these instances is unknown. However, they do provide insight into the convergence behavior, especially when compared between instances.

@@

\begin{table}
\centering
\scriptsize
\begin{tabular}{@{\bfseries}rrrrrrrrrrrr}
	\toprule
	\multicolumn{4}{c}{Instance} & \multicolumn{2}{c}{Properties} && \multicolumn{5}{c}{Results} \\
	\cmidrule(r){1-4} \cmidrule(lr){5-6} \cmidrule(lr){8-12}
	\normalfont{name} & $|\mathcal{J}|$ & $|\mathcal{T}|$ & $|\mathcal{M}|$ & $\max C_\text{job}$ &
	$C_\text{opt}$ && $\alpha$ & restarts & $\bar{C}$ & $C_\text{best}$ & $\bar{t}$ \\
	\midrule
	ft06 &  6 &  6 &  6 &   47 &   55 &&    0.9 & 1 &   55 &   55 &    0 \\[1ex]
	ft10 & 10 & 10 & 10 &  655 &  930 &&    0.9 & 5 &  954 &  941 &    2 \\
	     &    &    &    &      &      &&   0.99 & 5 &  943 &  938 &   18 \\
	     &    &    &    &      &      &&  0.999 & 5 &  933 &  930 &  182 \\[1ex]
	ft20 & 20 &  5 &  5 &  387 & 1165 &&    0.9 & 5 & 1215 & 1186 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 & 1182 & 1178 &   13 \\
	     &    &    &    &      &      &&  0.999 & 5 & 1170 & 1165 &  130 \\[1ex]
	c1   &  4 &  2 &  4 &   34 &   34 &&    0.9 & 1 &   34 &   34 &    0 \\
	c2   &  4 &  2 &  4 &   53 &   53 &&    0.9 & 1 &   53 &   53 &    0 \\
	c3   &  4 &  2 &  4 &  133 &  143 &&    0.9 & 1 &  143 &  143 &    0 \\
	c4   &  6 &  2 &  4 &   52 &   57 &&   0.99 & 5 &   57 &   57 &    2 \\
	c5   &  6 &  2 &  4 &  105 &  113 &&   0.99 & 5 &  113 &  113 &    2 \\
	c6   &  6 &  2 &  4 &  205 &  225 &&   0.99 & 5 &  225 &  225 &    2 \\
	c7   &  4 &  3 &  9 &   39 &   39 &&    0.9 & 1 &   39 &   39 &    0 \\
	c8   &  4 &  3 &  9 &   64 &   64 &&    0.9 & 1 &   64 &   64 &    0 \\
	c9   &  4 &  3 &  9 &  138 &  138 &&    0.9 & 1 &  138 &  138 &    0 \\
	c10  &  6 &  3 &  9 &   50 &   50 &&    0.9 & 1 &   50 &   50 &    0 \\
	c11  &  6 &  3 &  9 &  103 &  103 &&    0.9 & 1 &  103 &  103 &    0 \\
	c12  &  6 &  3 &  9 &  204 &  204 &&    0.9 & 1 &  204 &  204 &    0 \\
	c13  &  8 &  3 &  9 &  337 &  337 &&    0.9 & 5 &  337 &  337 &    0 \\
	c14  &  8 &  3 &  9 &  705 &  705 &&    0.9 & 5 &  705 &  705 &    0 \\
	c15  &  8 &  3 &  9 & 1458 & 1458 &&    0.9 & 5 & 1458 & 1458 &    0 \\
	c16  & 10 &  4 & 16 &  405 &  405 &&    0.9 & 5 &  405 &  405 &    0 \\
	c17  & 10 &  4 & 16 &  955 &  955 &&    0.9 & 5 &  955 &  955 &    0 \\
	c18  & 10 &  4 & 16 & 1621 & 1621 &&    0.9 & 5 & 1621 & 1621 &    0 \\
	c19  & 15 &  5 & 25 & 2631 & 2631 &&    0.9 & 5 & 2631 & 2631 &    0 \\[1ex]
	v20  &  8 &  2 &  4 &  176 &      &&    0.9 & 5 &  387 &  387 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 &  387 &  387 &    7 \\
	     &    &    &    &      &      &&  0.999 & 5 &  387 &  387 &   67 \\[1ex]
	v21  &  8 &  2 &  8 &  187 &  187 &&    0.9 & 5 &  204 &  188 &    0 \\
	     &    &    &    &      &      &&   0.99 & 5 &  197 &  188 &    4 \\
	     &    &    &    &      &      &&  0.999 & 5 &  188 &  187 &   25 \\[1ex]
	v22  &  8 &  4 &  8 &  195 &      &&    0.9 & 5 &  237 &  237 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 &  237 &  237 &    9 \\
	     &    &    &    &      &      &&  0.999 & 5 &  237 &  237 &   82 \\[1ex]
	v30  & 16 &  2 &  4 &  666 &      &&    0.9 & 5 & 2382 & 2381 &   10 \\
	     &    &    &    &      &      &&   0.99 & 5 & 2381 & 2381 &  102 \\
	     &    &    &    &      &      &&  0.999 & 5 & 2381 & 2381 & 1045 \\[1ex]
	v31  & 16 &  2 &  8 &  566 &      &&    0.9 & 5 &  963 &  961 &   12 \\
	     &    &    &    &      &      &&   0.99 & 5 &  960 &  959 &  126 \\
	     &    &    &    &      &      &&  0.999 & 5 &  958 &  956 & 1238 \\[1ex]
	v32  & 16 &  4 &  8 &  655 &      &&    0.9 & 5 & 1119 & 1116 &   11 \\
	     &    &    &    &      &      &&   0.99 & 5 & 1112 & 1111 &  116 \\
	     &    &    &    &      &      &&  0.999 & 5 & 1108 & 1106 & 1164 \\[1ex]
	v33  & 16 &  4 & 16 &  626 &  626 &&    0.9 & 5 &  628 &  626 &    5 \\
	     &    &    &    &      &      &&   0.99 & 5 &  657 &  651 &   84 \\[1ex]
	\bottomrule
\end{tabular}
\caption{Computational results for the FJS}
\label{table:fjs}
\end{table}

@@

\begin{table}
\centering
\scriptsize
\begin{tabular}{@{\bfseries}rrrrrrrrrrrrr}
	\toprule
	& FJS & FBJS & && \multicolumn{2}{c}{Critical Path} &&
	\multicolumn{2}{c}{Naive shift} && \multicolumn{2}{c}{Both} \\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){6-7}
	\cmidrule(lr){9-10} \cmidrule(lr){12-13}
	\normalfont{name} & $C_\text{best}$ & $C_\text{opt}$ & $\alpha$ && $\bar{C}$ & $C_\text{best}$ &&
	$\bar{C}$ & $C_\text{best}$ && $\bar{C}$ & $C_\text{best}$ \\
	\midrule
	ft06 &   55 &   63 &  0.99 &&  102 &   95 &&   64 &   63 &&   66 &   63 \\[1ex]
	ft10 &  930 & 1068 &   0.9 && 2183 & 1931 && 1507 & 1436 && 1464 & 1415 \\
	     &      &      &  0.99 && 2139 & 1931 && 1444 & 1353 && 1413 & 1349 \\
	     &      &      & 0.999 && 2366 & 2028 && 1380 & 1281 && 1371 & 1292 \\[1ex]
	ft20 & 1165 &      &   0.9 && 2476 & 2406 && 1957 & 1866 && 1935 & 1869 \\
	     &      &      &  0.99 && 2454 & 2348 && 1840 & 1814 && 1860 & 1840 \\
	     &      &      & 0.999 && 2393 & 2209 && 1694 & 1646 && 1714 & 1632 \\[1ex]
	c1   &   34 &      &  0.99 &&   66 &   62 &&   37 &   37 &&   37 &   37 \\
	c2   &   53 &      &  0.99 &&   88 &   75 &&   65 &   65 &&   65 &   65 \\
	c3   &  143 &      &  0.99 &&  206 &  206 &&  180 &  180 &&  180 &  180 \\
	c4   &   57 &      &  0.99 &&  116 &  109 &&   94 &   92 &&   91 &   90 \\
	c5   &  113 &      &  0.99 &&  247 &  215 &&  180 &  170 &&  175 &  170 \\
	c6   &  225 &      &  0.99 &&  502 &  434 &&  365 &  360 &&  360 &  353 \\
	c7   &   39 &   39 &  0.99 &&   39 &   39 &&   39 &   39 &&   39 &   39 \\
	c8   &   64 &   64 &  0.99 &&   64 &   64 &&   64 &   64 &&   64 &   64 \\
	c9   &  138 &  138 &  0.99 &&  138 &  138 &&  138 &  138 &&  138 &  138 \\
	c10  &   50 &   50 &  0.99 &&   50 &   50 &&   50 &   50 &&   50 &   50 \\
	c11  &  103 &      &  0.99 &&  170 &  116 &&  106 &  106 &&  106 &  106 \\
	c12  &  204 &      &  0.99 &&  265 &  210 &&  208 &  208 &&  208 &  208 \\
	c13  &  337 &      &  0.99 &&  557 &  524 &&  467 &  458 &&  393 &  389 \\
	c14  &  705 &      &  0.99 && 1203 & 1036 &&  866 &  833 &&  797 &  788 \\
	c15  & 1458 &      &  0.99 && 2556 & 2258 && 1789 & 1666 && 1508 & 1493 \\
	c16  &  405 &  405 &  0.99 &&  519 &  483 &&  444 &  429 &&  405 &  405 \\
	c17  &  955 &  955 &  0.99 && 1257 & 1009 &&  962 &  955 &&  955 &  955 \\
	c18  & 1621 & 1621 &  0.99 && 2314 & 2131 && 1710 & 1688 && 1621 & 1621 \\
	c19  & 2631 & 2631 &  0.99 && 4568 & 3973 && 4365 & 4049 && 2631 & 2631 \\[1ex]
	v20  &  387 &      &   0.9 &&  571 &  540 &&  494 &  476 &&  438 &  423 \\
	     &      &      &  0.99 &&  527 &  517 &&  447 &  421 &&  424 &  418 \\
	     &      &      & 0.999 &&  557 &  497 &&  427 &  425 &&  419 &  416 \\[1ex]
	v21  &  187 &      &   0.9 &&  331 &  293 &&  277 &  254 &&  218 &  215 \\
	     &      &      &  0.99 &&  327 &  291 &&  213 &  209 &&  198 &  194 \\
	     &      &      & 0.999 &&  335 &  313 &&  196 &  194 &&  195 &  194 \\[1ex]
	v22  &  237 &      &   0.9 &&  419 &  387 &&  326 &  314 &&  294 &  284 \\
	     &      &      &  0.99 &&  393 &  369 &&  293 &  281 &&  273 &  262 \\
	     &      &      & 0.999 &&  413 &  367 &&  273 &  271 &&  264 &  259 \\[1ex]
	v30  & 2381 &      &   0.9 && 4210 & 4068 && 5969 & 5856 && 3546 & 3438 \\
	     &      &      &  0.99 && 4200 & 4154 && 5591 & 5411 && 3287 & 3147 \\
	     &      &      & 0.999 && 4150 & 4142 && 5339 & 5232 && 3334 & 3276 \\[1ex]
	v31  &  959 &      &   0.9 && 1658 & 1573 && 4303 & 4133 && 1702 & 1635 \\
	     &      &      &  0.99 && 1688 & 1632 && 3772 & 3712 && 1646 & 1617 \\
	     &      &      & 0.999 && 1702 & 1656 && 3553 & 3444 && 1479 & 1391 \\[1ex]
	v32  & 1111 &      &   0.9 && 2570 & 2389 && 5214 & 5054 && 2570 & 2389 \\
	     &      &      &  0.99 && 2629 & 2601 && 4481 & 4209 && 2171 & 1983 \\
	     &      &      & 0.999 && 2595 & 2451 && 3614 & 3005 && 1953 & 1907 \\[1ex]
	v33  &  626 &      &   0.9 && 1296 & 1212 && 3182 & 2931 && 1098 & 1053 \\
	     &      &      &  0.99 && 1335 & 1244 && 2061 & 1903 &&  952 &  894 \\
	\bottomrule
\end{tabular}
\caption{Computational results for the FBJS}
\label{table:fbjs}
\end{table}
